Amendments Summary

### 2025-01-03 Thesis/amend_v2.qmd
update the summary

In Chapter 2, the data plot is compared against 19 null plots because humans are not well-suited to evaluating lineups with a large number of plots. To ensure reliable results, such a lineup should ideally be assessed by at least five subjects; otherwise, the smallest possible $p$-value of the test may not be sufficiently small. Moreover, involving multiple subjects helps reduce variability in individuals' abilities to evaluate residual plots.

In contrast, computer vision models can evaluate lineups with as many null plots as desired, which is one of their advantages. **XXX Have you made any modifications in the thesis to make these points so that the reader is not likely to ask the same question as Daniela? If so, this needs to be stated here.**

>>>>

In Chapter 2, the data plot is compared against 19 null plots, as humans are not well-suited to evaluating lineups with a large number of plots. For reliable results, such a lineup should ideally be evaluated by at least five participants; otherwise, the smallest achievable $p$-value may not be sufficiently small. Additionally, involving multiple participants helps mitigate variability in individuals' abilities to assess residual plots. This approach is discussed in the experimental design and is supported by the cited literature in the chapter, such as Validation of Visual Statistical Inference, Applied to Linear Models by Mahbubul Majumder, Heike Hofmann, and Dianne Cook.

I decided not to modify this chapter further, as it has been submitted published.
